---
title: "Chapter 2"
author: "Alice Pierce"
date: "8/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Given the following data frame, how do I create a new column called “3” that contains the sum of 1 and 2? You may only use $, not [[. What makes 1, 2, and 3 challenging as variable names?

```{r}
df <- data.frame(runif(3), runif(3))
names(df) <- c(1, 2)
#answer
df$`3` <- df$`1`+df$`2`
```

In the following code, how much memory does y occupy?

```{r}
x <- runif(1e6)
y <- list(x, x, x)
#24 Mb
```

On which line does a get copied in the following example?
```{r}
a <- c(1, 5, 3, 2)
b <- a
b[[1]] <- 10
#second line
```

```{r}
library(lobstr)
```

```{r}
x <- c(1, 2, 3)
y <- x
obj_addr(x)
#> [1] "0x7fe11b31b1e8"
obj_addr(y)
#> [1] "0x7fe11b31b1e8"
```

#obj_address allows us to access the object's identifier --> location in memory where the object is stored which is referred to with an identifier. Inr eality, the actual memory addresses changes every time the code is run. 
#identifiers change every time you restart R

```{r}
?Reserved
```

Explain the relationship between a, b, c and d in the following code:
```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10
```

#binding a vector of values (1:10) to name, a. b is referencing a. c is referencing b (and thus, a). a,b,c point to the same address in memory. d is another name for a vector of values (1:10) but has a different address in memory.

The following code accesses the mean function in multiple ways. Do they all point to the same underlying function object? Verify this with lobstr::obj_addr().
##stuck :( 
```{r}
obj_address(mean)
obj_address(base::mean)
obj_address(get("mean"))
obj_address(evalq(mean))
obj_address(match.fun("mean"))
```

By default, base R data import functions, like read.csv(), will automatically convert non-syntactic names to syntactic ones. Why might this be problematic? What option allows you to suppress this behaviour?
#might override base R or functions in libraries
#idk how to suppress the behavior :( 

What rules does make.names() use to convert non-syntactic names into syntactic ones?
#uses letters(ASCII), numbers and dot or underline characters. always start with a letter or dot (not followed by number) 

I slightly simplified the rules that govern syntactic names. Why is .123e1 not a syntactic name? Read ?make.names for the full details.
#dot cannot be followed by number

```{r}
x <- c(1, 2, 3)
y <- x

y[[3]] <- 4
x
#> [1] 1 2 3
```

```{r}
x <- c(1, 2, 3)
cat(tracemem(x), "\n")
#> <0x7f80c0e0ffc8> 
```

```{r}
y <- x
y[[3]] <- 4L
#> tracemem[0x7f80c0e0ffc8 -> 0x7f80c4427f40]: 
```

```{r}
y[[3]] <- 5L

untracemem(x)
```

```{r}
f <- function(a) {
  a
}

x <- c(1, 2, 3)
cat(tracemem(x), "\n")
#> <0x7fe1121693a8>

z <- f(x)
# there's no copy here!

untracemem(x)
```

```{r}
l1 <- list(1, 2, 3)
```
#lists store references to the values, not the values themselves

```{r}
l2 <- l1
l2[[3]] <- 4
```
#l2 first two objects reference the same two objects as l1, but they reference a different object on the third pos (3 vs 4)

```{r}
ref(l1, l2)
#> █ [1:0x7fe11166c6d8] <list> 
#> ├─[2:0x7fe11b6d2078] <dbl> 
#> ├─[3:0x7fe11b6d2040] <dbl> 
#> └─[4:0x7fe11b6d2008] <dbl> 
#>  
#> █ [5:0x7fe11411cc18] <list> 
#> ├─[2:0x7fe11b6d2078] 
#> ├─[3:0x7fe11b6d2040] 
#> └─[6:0x7fe114130a70] <dbl>
```

```{r}
d1 <- data.frame(x = c(1, 5, 6), y = c(2, 4, 3))
```

```{r}
d2 <- d1
d2[, 2] <- d2[, 2] * 2
```
#If you modify a column, only that column needs to be modified; the others will still point to their original references
#However, if you modify a row, every column is modified, which means every column must be copied

```{r}
x <- c("a", "a", "abc", "d")
```

#R uses a global string pool where each element of a character vector is a pointer to a unique string in the pool

```{r}
ref(x, character = TRUE)
#> █ [1:0x7fe114251578] <chr> 
#> ├─[2:0x7fe10ead1648] <string: "a"> 
#> ├─[2:0x7fe10ead1648] 
#> ├─[3:0x7fe11b27d670] <string: "abc"> 
#> └─[4:0x7fe10eda4170] <string: "d">
```

Why is tracemem(1:10) not useful?

```{r}
tracemem(1:10)
```
#there's no object to be traced

Explain why tracemem() shows two copies when you run this code. Hint: carefully look at the difference between this code and the code shown earlier in the section.

```{r}
x <- c(1L, 2L, 3L)
tracemem(x)

x[[3]] <- 4
```
#hmm idk :( 

Sketch out the relationship between the following objects:
```{r}
a <- 1:10
b <- list(a, a)
c <- list(b, a, 1:10)
```
#b points to 2 a
#c points to b, a, and a object of 1:10
What happens when you run this code?
```{r}
x <- list(1:10)
x[[2]] <- x
```
#x holds a list of reference values of 1:10
#x now contains 2 lists, and the second list has the same reference values as above

##sorry i could not finish :( 

